\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-20 paper/main.tex
left comment

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning~(DL)
  libraries, such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DL libraries hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DL library testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

@@

\Fix{What evaluation can be added to this section?}
\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}

@@

% \Fix{Consider the comments from Saikat, please.}
Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug. Then it proceeds to run the entire testing tool on the enviroment. After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool. In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.

@@

\Fix{Abid: Added, please revise}

\section{\tname: Use cases}

We anticipate two major use cases for \tname: (1) \textbf{evaluation
  of testing techniques} and (2) \textbf{evaluation of repair
  techniques}. Dozens of API- and model-level testing techniques have
been proposed in the literature recently and it is imperative to
evaluate them using a standard benchmark. \tname\ provides such
benchmark. Considering repair, as testing techniques mature it becomes
important to identify candidate repairs that can be recommended to
developers when reporting issues in bug trackers. With \tname\ it is
possible to identify if the problem has been resolved. 
\Fix{The concept of repairing has not been tied to any commands in the tool. Suggestions include
a way to recreate an enviroment with the bug fixed, or a way to check if the bug has been fixed in a new version of the library.}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning~(DL)
  libraries, such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DL libraries hinders credible evaluation of
  these techniques. We present \tname, a database of curated
  reproducible bugs to fill that gap. Unique challenges exist in this
  context, such as installing drivers of specific CUDA versions to
  reproduce certain GPU-related bugs.
  %% enable credible  evaluation of bug-finding DL library testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

@@

\Fix{What evaluation can be added to this section?}
\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}\label{sec:running-free-fuzz}

@@

% \Fix{Consider the comments from Saikat, please.}
Initially, the script reproduces the bug and updates the environment
inside the docker container of FreeFuzz to match the enviroment of the
bug. Then, it proceeds to run the entire testing tool on the
enviroment.

\Fix{Abid, this does not make sense to me. If you are checking this
  manually, you could run FreeFuzz separately and check manually. What
  is the point?! You need to provide a list of bugs and check
  automatically how many the tool can find (based on some criteria,
  e.g, match the error message in Assertion or some n frames in the
  stack (for crash)). --Marcelo}
After the execution completes, the output can be
checked for all failures produced by FreeFuzz (saved inside the
container) and manually inspected to see if any failure that can
reveal the bug in question was generated by the tool. In this case,
the failure generated by FreeFuzz could not generate a failure that
can reveal this bug since the API "torch.\_dynamo.export" is not
supported by FreeFuzz.

@@

%% \Fix{Abid: Added, please revise}
%% \section{Use case: Evaluation of testing techniques}
%% The primary use case of \tname\ is the evaluation of testing
%% techniques. Dozens of API- and model-level testing techniques have
%% been proposed in the literature recently and it is imperative to
%% evaluate them using a standard
%% benchmark. Section~\ref{sec:running-free-fuzz} elaborates on how to
%% integrate a testing tool, such as FreeFuzz~\cite{wei2022free}, into
%% \tname.

%% We anticipate two major use cases for \tname: (1) \textbf{} and (2) \textbf{evaluation of repair
%%   techniques}. Considering repair, as testing techniques mature it becomes
%% important to identify candidate repairs that can be recommended to
%% developers when reporting issues in bug trackers. With \tname\ it is
%% possible to identify if the problem has been resolved. 
%% \Fix{The concept of repairing has not been tied to any commands in the tool. Suggestions include
%% a way to recreate an enviroment with the bug fixed, or a way to check if the bug has been fixed in a new version of the library.}
